Ladies' figure skating in the 2002 Winter Olympics

### 2022-10-17 inst/skating.Rmd
name every chunk, also change title

---
title: "skating"
output: bookdown::html_document2
---

@@

# Ladies' figure skating in the 2002 Winter Olympics

This document analyses strengths of the competitors in the Ladies'
Figure Skating at the 2002 Winter Olympics.  In the package, dataframe
`skating_table` is copied from Lock and Lock (see skating.Rd for more
details).  It also creates file `data/skating.rda` which contains R
objects `skating`, `skating_table`, and `skating_maxp`.

@@

```{r,dpi=72}
dotchart(m)
dotchart(log(m))
```

@@

```{r}
mgv  - max(out[4:6])
```

@@

```{r}
plot(out,ylab="log likelihood",axes=FALSE)
axis(2)
axis(side=1,at=1:6,srt=45,labels=c(
"Hug<Coh", "Slu<Coh", "Kwa<Coh",
"Hug<Sug", "Slu<Sug", "Kwa<Sug"
))
```

@@

```{r}
skating_table
o <- ordertable_to_ranktable(skating_table)
o
```

```{r}
class(o) <- "matrix"
o
```

Select just the top seven:
```{r}
o <- o[,1:7]
o
```

@@

```{r}
o <- t(apply(o,1,rank))
colnames(o) <- rownames(skating_table)[1:7]
o
```

@@

```{r}
class(o) <- "ranktable"
o
```

@@

```{r}
o <- ranktable_to_ordertable(o)
o
```

@@

```{r}
o <- ordertable2supp(o)
o
```
and have some fun with it:

```{r}
(o <- maxp(o))
pie(o)
```

>>>>

---
title: "Ladies' figure skating in the 2002 Winter Olympics"
output: bookdown::html_document2
---

@@

This document analyses Bradley-Terry strengths of the competitors in
the Ladies' Figure Skating at the 2002 Winter Olympics.  In the
package, dataframe `skating_table` is copied from Lock and Lock (see
skating.Rd for more details).  It also creates file `data/skating.rda`
which contains R objects `skating`, `skating_table`, and
`skating_maxp`.

@@

```{r,dotchartm,dpi=72}
dotchart(m)
dotchart(log(m))
```

@@

```{r subtractmaxfrommgv}
mgv  - max(out[4:6])
```

@@

```{r plotrestrictedlikes}
plot(out,ylab="log likelihood",axes=FALSE)
axis(2)
axis(side=1,at=1:6,srt=45,labels=c(
"Hug<Coh", "Slu<Coh", "Kwa<Coh",
"Hug<Sug", "Slu<Sug", "Kwa<Sug"
))
```

@@

```{r justtop7}
skating_table
o <- ordertable_to_ranktable(skating_table)
o
```

```{r setclasstomatrix}
class(o) <- "matrix"
o
```

Select just the top seven:
```{r selectthetop7}
o <- o[,1:7]
o
```

@@

```{r replaceranks}
o <- t(apply(o,1,rank))
colnames(o) <- rownames(skating_table)[1:7]
o
```

@@

```{r coercetoranktble}
class(o) <- "ranktable"
o
```

@@

```{r thenceto}
o <- ranktable_to_ordertable(o)
o
```

@@

```{r makelikef}
o <- ordertable2supp(o)
o
```
and have some fun with it:

```{r plotapieofo}
(o <- maxp(o))
pie(o)
```
